---
title: "Competing Hazards Simulation"
author: "Britney He"
date: "11/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(deSolve)
library(reshape2)
library(ggplot2)
```

## 
The model we want to specify in this etivity has 3 compartments: I (infected), R (recovered) and M (dead). 
Infected people can recover at a rate $\gamma$, and die (transition to the M compartment) at a rate $\mu$ .

The differential equations for this model look like this:
dI/dt = $-\gamma I - \mu I$
dR/dt = $\gamma I$
dM/dt = $\mu I$

## The model function:

```{r}
cohort_model - function(time, state, parameters) {  
    with(as.list(c(state, parameters)), {  
    # The differential equations
      dI = -gamma * I - mu * I  
      dR = gamma * I           
      dM = mu * I               
    return(list(c(dI, dR, dM))) 
    })
}
```


```{r}
initial_state_values = c(I = 1000000,    # at the start, there are 10^6 infected people
                          R = 0,         # no one has recovered
                          M = 0)         # no one has died 
parameters = c(gamma = 0.1, mu = 0.2)          
times = seq(from = 0, to = 4*7, by = 1) # model the course of the infection over 4 weeks = 4*7 days
```

## Q: After 4 weeks, do you expect more people to have recovered or more people to have died, and why?
We expect more people to die than to recover because the mortality rate (0.2) is higher than the recovery rate (0.1), so people move more quickly from I  to M than from I to R.


```{r}
# Solving differential equations:
output = as.data.frame(ode(y = initial_state_values, 
                            times = times, 
                            func = cohort_model,
                            parms = parameters))
output_long = melt(as.data.frame(output), id = "time")     

# Plot
ggplot(data = output_long,   
       aes(x = time, y = value, colour = variable, group = variable)) + geom_line() + xlab("Time (days)") + ylab("Number of people") +labs(colour = "Compartment") 
```


## Q: Based on the model output, what proportion of the initially infected cohort died before recovering over the 4 week period?

```{r}
output
output[output$time == 28,]
# Divide the number of people who died over the 4 week period by the number of people initially infected:
output[29,"M"]/1000000
```
