---
title: "SIR Modeling: Infected Cohort"
author: "Britney He"
date: "11/29/2020"
output: html_document
---
This task is to find out how long it takes for a cohort of infected people to recover. 
To answer this question, we need to keep track of 2 populations: 
those that are infected (compartment $I$), and those that have recovered (compartment $R$). 
Infected people recover at a rate $\gamma$ (*gamma*). The differential equations describing this are:

\begin{align}
\frac{dI}{dt} & = -\gamma I \\
\frac{dR}{dt} & = \gamma I
\end{align}

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(deSolve)   # package to solve the model
library(reshape2)  # package to change the shape of the model output
library(ggplot2)   
```

## Initial condition:
We are looking at a cohort of $10^6$ currently infected people, and no one has recovered so far. The average duration of infection is 10 days.
Q: how many people will recover from the infection over a 4-week period?

```{r}
initial_number_infected = 1000000         # initial infected population size
initial_number_recovered = 0              # initial number of people in the recovered state
recovery_rate = 0.1                       # rate of recovery gamma in units of days^-1
follow_up_duration = 28                   # duration to run the model for in units of days

# Combine into the model input vectors:
initial_state_values <- c(I = initial_number_infected, 
                          R = initial_number_recovered)  
parameters <- c(gamma = recovery_rate)  
times <- seq(from = 0, to = follow_up_duration, by = 1) 
```

## Specifying the model function:
```{r}
cohort_model = function(time, state, parameters) {   
    with(as.list(c(state, parameters)), {  
      dI <- -gamma * I
      dR <- gamma * I
    return(list(c(dI, dR)))                           
    })
}
```

## Further explanations:
When using deSolve, every model function takes as input arguments
1) time: the timesteps that we want to solve the model at
2) state: storing the number of people in each compartment at each timestep
3) parameters: names and values of model parameters, e.g. the rates of transition between compartments

with(as.list(c(state, parameters)), {...} tells R to look within the objects containing our state variables and parameters (by combining and converting them to a list object), so that you can refer to them directly. 
In other words, we can unpack the state variables specified in "state" and the model parameters specified in "parameters" using the with() command, for our convenience.

## Solving the model equations:
```{r}
output = as.data.frame(ode(y = initial_state_values, 
                            times = times, 
                            func = cohort_model,
                            parms = parameters))
# ode = ordinary differential equations
output
```

## Q: Based on the output, how many people have recovered after 4 weeks?
```{r}
output[output$time == 28, c("time","R")]  
```


## Q: What proportion of the total population does this correspond to?
```{r}
output[output$time == 28,"R"]/(output[output$time == 28,"I"] + output[output$time == 28,"R"])
```

## Q: Plotting the output
```{r}
# turn output dataset into a long format, so that the number in each compartment at each timestep are all in the same column
output_long <- melt(as.data.frame(output), id = "time")                  

# Plot the number of people in each compartment over time
ggplot(data = output_long,          
       aes(x = time, y = value, colour = variable, group = variable)) +  
  geom_line() + xlab("Time (days)") + ylab("Number of people") +                    
  labs(title = paste("Number infected and recovered over time when gamma =",
               parameters["gamma"],"days^-1")) 
```


## Q: Based on the plot, at what timepoint were infected and recovered individuals equal in number?
```{r}
# Answer: around 7 days - this where the I and R lines intersect.

# the number in the I and R compartment are very similar at timestep 7.
output[output$time == 7,]
```


Varying $\gamma$: 

Average duration of infection = 2 days so the recovery rate = 1/2 = 0.5 $days^−1$

```{r}
parameters <- c(gamma = 0.5)

# Solving the model
output <- as.data.frame(ode(y = initial_state_values, 
                            times = times, 
                            func = cohort_model,
                            parms = parameters))

# Turn output dataset into long format
output_long <- melt(as.data.frame(output), id = "time")   

# Plotting the output
ggplot(data = output_long,       
       aes(x = time, y = value, color = variable, group = variable)) +  
  geom_line() + xlab("Time (days)") + ylab("Number of people") +
  labs(title = paste("Number infected and recovered over time when gamma =",
                      parameters["gamma"],"days^−1")) + 
  scale_color_brewer(palette = "Set1")
```

Average duration of infection = 20 days so the recovery rate = 1/20 = 0.05 $days^−1$
```{r}
parameters <- c(gamma = 0.05)

# Solving the model
output <- as.data.frame(ode(y = initial_state_values, 
                            times = times, 
                            func = cohort_model,
                            parms = parameters))

# Plotting the output
output_long <- melt(as.data.frame(output), id = "time") 

ggplot(data = output_long,                                 
       aes(x = time, 
           y = value, 
           colour = variable, 
           group = variable)) +  geom_line() + xlab("Time (days)") + ylab("Number of people") +    
  labs(title = paste("Number infected and recovered over time when gamma =",
                    parameters["gamma"],"days^-1")) 
```

## Q: What changes do you observe in the transition to the recovered compartment if `gamma` is higher or lower?
Answer: if the rate is higher ($\gamma$ = 0.5), we can see that infected people recover more quickly: it takes less than 2 days for half of the infected cohort to recover, and by around 8 days, nearly everyone has recovered. A lower rate ($\gamma$ = 0.05) on the other hand corresponds to a slower transition: it takes around 14 days for half of infected people to move into the R compartment, and by the end of our 4 week follow-up around a quarter of people still have not recovered.