---
title: "SIR Model with Dynamic Force of Infection"
author: "Britney He"
date: "11/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(deSolve)
library(reshape2)
library(ggplot2)
```

The differential equations for this model look like this:
dS/dt = $-\beta S I/N$
dI/dt = $\beta$ $I/N$ $S$ $-\gamma I$
dR/dt = $\gamma I$

## Assumptions:

1) a homogeneous population - everyone in the same compartment is subject to the same hazards
2) a well-mixed population - all susceptible people have the same risk as getting infected, dependent on the number of infected people
3) a closed population - there are no births or deaths, so the population size stays constant

```{r}
# MODEL INPUTS:
# at timestep 0
initial_state_values = c(S = 999999, I = 1, R = 0) 

parameters = c(beta = 1,      # the infection rate
              gamma = 0.1)    # the rate of recovery

# TIMESTEPS:
times = seq(from = 0, to = 60, by = 1)   

# SIR MODEL FUNCTION: 
sir_model = function(time, state, parameters) {  
    with(as.list(c(state, parameters)), {  
      N = S+I+R 
      lambda = beta * I/N
      dS = -lambda * S             
      dI = lambda * S - gamma * I    
      dR = gamma * I                
    return(list(c(dS, dI, dR))) 
    })
}

# MODEL OUTPUT (solving the differential equations):
output = as.data.frame(ode(y = initial_state_values, 
                            times = times, 
                            func = sir_model,
                            parms = parameters))
```

## Plot
```{r}
output_long = melt(as.data.frame(output), id = "time")              

ggplot(data = output_long, aes(x = time, y = value, colour = variable, group = variable)) + 
  geom_line() +  xlab("Time (days)") + ylab("Number of people") + labs(colour = "Compartment")                    
```


Q: How does the pattern of the epidemic change under different assumptions for $\beta$ and $\gamma$, e.g. in terms of the peak of the epidemic, the number infected at the peak, and when the epidemic ends?

A: With $\gamma$ held constant at 0.1, an increasing value for $\beta$ leads to an earlier and higher peak of infected people. With a higher $\beta$, the peak is also "sharper", i.e. the epidemic also starts to decline again more quickly. A $\beta$ of 0.1 actually does not give rise to an epidemic: the number of susceptible, infected and recovered people stays the same as at the beginning.

A: Different recovery rates affect the epidemic just as much as different forces of infection. With $\beta$ held constant at 1, an increasing value for $\gamma$ tends to lead to a later and lower peak of infected people, and an earlier rise in the recovered curve. If people can stay infected for a long time before recovering ($\gamma$ = 0.025, corresponding to an average duration of infection of 40 days), the number of infected people stays high over a longer period and declines slowly - the epidemic flattens out. In contrast, if recovery happens very quickly after infection ($\gamma$ = 0.5), there is a only small peak in the prevalence of infection and the epidemic dies out quickly. If $\gamma$ is as large as 1, no epidemic takes place after the introduction of 1 infected case.

